---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# flights.dashboard

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of flights.dashboard is to apply some of what is explained on the fantastic book [Engineering Production-Grade Shiny Apps](https://engineering-shiny.org/) by Colin Fay, Sébastien Rochette, Vincent Guyader and Cervan Girard, using as basis the post [A beginner's guide to Shiny modules](https://emilyriederer.netlify.app/post/shiny-modules/) by Emily Riederer.

See ["How this app/package was created?"](https://ggpinto.github.io/flights.dashboard/articles/flights-dashboard.html) for more details.

## Result

The end result can be seen on https://ggpinto.shinyapps.io/flights/.

Or you can also install the the application from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ggpinto/flights.dashboard")
```

And then run it locally with:

```{r, eval = FALSE}
flights.dashboard::run_app()
```

## Code of Conduct

Please note that the flights.dashboard project is released with a [Contributor Code of Conduct](https://ggpinto.github.io/flights.dashboard/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
